---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = FALSE
)
library(tidyverse)
library(diversity.tool)
```

# diversity.tool <a href='https://github.com/PaulESantos/diversity.tool'></a>

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![CRAN status](https://www.r-pkg.org/badges/version/ppendemic)](https://CRAN.R-project.org/package=ppendemic)
[![Travis build status](https://travis-ci.com/PaulESantos/ppendemic.svg?branch=main)](https://travis-ci.com/PaulESantos/ppendemic)
<!-- badges: end -->

The goal of diversity.tool is to ...

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("PaulESantos/diversity.tool")
```
## Example

This is a basic example which shows you how to solve a common problem:

- Transform community matrix to tibble:

```{r example}
library(diversity.tool)
library(vegan)
data("dune")
dune_tbl <- dune %>% comm_to_tbl()
dune_tbl
```

- Or build a community matrix from a tibble:

```{r example_1}
dune_comm <- dune_tbl %>% 
  tbl_to_comm(site, species, abundance)
dune_comm[1:6, 1:6]
```

- IVI index

```{r ivi}

data("bci")

bci %>% 
  ivi_index(sub_plot, species, area_basal)

```


- Rank-abundance calculation:

  + All sample units as one community
```{r rankabun}
dune %>% 
  rankabund()
```
  
   + Each sample units as a different community

```{r rankabun1}
dune %>% 
  rankabund(group = "site")
```

  +Rank-abundance plot

```{r rankabun_plot}
dune %>% 
  rankabund_plot()
```

- Transform a `dist` matrix to tibble:

```{r distbl}

dune_dist <- vegdist(dune[1:10, 1:10])

dune_dist


dune_dist_tbl <- dune_dist %>% 
  as_distbl()

dune_dist_tbl
```

- Transform to long format:

```{r longtbl}

dune_dist_tbl %>% 
  long_distbl()

```



## Citation

To cite the ppendemic package, please use:

```{r}
citation("diversity.tool")
```
